---
title: "Exponential Distribution and Compairing with CLT"
author: "Vasudha Singh"
date: "December 6, 2018"
output:
  word_document: default
  pdf_document: default
---  

install.packages("knitr")
install.packages("markdown")
install.packages("rmarkdown")  


```{r echo=FALSE, message=FALSE, warning=FALSE}   
library(ggplot2) 
```


## Overview 

In this project we will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. For analysis purpose, we will set lambda = 0.2 for all of the simulations and this investigation will compare with the distribution of averages of 40 exponentials over 1000 Simulations.

##Simulations

Set the simulation variables and Run Simulation 

```{r, echo=TRUE}
set.seed(6817)
n<-40
lambda<-0.2
nosim<-1000  

simMeans <- NULL  
for(i in 1:1000) simMeans= c(simMeans, mean(rexp(n, lambda)))  
```  

## Sample mean Versus Theoretical mean 
###Sample Mean  
Calculating mean from Simulations  

```{r}  
 mean(simMeans)  
```  

###Theoretical Mean  
Calculating mean of Exponential distribution , whose mean is 1/ lambda  

```{r}  
 expMeans<-1/lambda  
 expMeans
```  
###Comparison between Sample Mean and Theoretical Mean  

```{r}  
 abs(mean(simMeans)-expMeans)  
```  

This shows that the Center of distribution of Sample Mean `r mean(simMeans)` is closely related to Theoretical Mean `r expMeans`.  


## Sample Variance Versus Theoretical Variance  
###Sample Variance  
Calculating Variance and Standard deviation from Simulations   

```{r}  
 var(simMeans)  
 sd(simMeans)  
```  

###Theoretical Variance   
Calculating Variance of Exponential distribution and standard deviation  

```{r}  
 expVariance<-(1/lambda)^2/(n)   
 expVariance
 expStdev<- 1/(lambda*sqrt(n))  
 expStdev
```  
###Comparison between Sample Variance and Theoretical Variance  

```{r}  
abs(var(simMeans)-expVariance)  
```  
This shows that the variability  of distribution of Sample Variance `r var(simMeans)` is closely related to Theoretical Variance `r expVariance`.  

##Distribution  
###Show that distribution is approximately Normal.  
The Histogram plot of the means of 1000 simulations is overlaid with the normal distribution with mean `r expMeans` and standard deviation `r expStdev`.  
This shows the distribution of simulation is normal.  

```{r}  
g<-ggplot(data.frame(y=simMeans), aes(x=y))  
g<- g+ geom_histogram(aes(y=..density..), binwidth= 0.2, fill="blue", color="red") +
  stat_function(fun=dnorm,args=list(mean=expMeans, sd=expStdev), size=2)+
  ggtitle('Simulation Plot')+ xlab('Simulation mean')+ ylab('density')  
g

```  